\mytitle

### 2021-12-27 paper.tex
improve wording

In the following an ILP-aware implementation of the real dilogarithm
is presented, which allows for the simultaneous execution of multiple
floating\-/point operations.  The real dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\ln(1-t)}{t} \, \textnormal{d}t, &
  &x<1.
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
  \label{eq:series}
\end{align}
%
Further series representations exist, for example the accelerated
series
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\ln(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A series representation in
terms of Chebyshev polynomials of the first kind $T_n(x)$ is given in
\cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n(2x-1),
  \label{eq:cheby}
\end{align}
%
which is used for example in the ROOT program library \cite{root}.
The r.h.s.\ of Eqs.~\eqref{eq:series}--\eqref{eq:cheby} can be summed,
for example, using Horner's scheme or Clenshaw's algorithm
\cite{clenshaw}, respectively.  These summation techniques are,
however, purely sequential and thus do not make use of ILP.  In the
following an approximant of the real dilogarithm is presented, which
makes use of ILP, using a rational function approximation in
combination with Estrin's scheme, similar to the approach used in
Eq.~\eqref{eq:mixed}.

@@

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level (ILP) parallelism.  We found that a
rational minimax approximant in combination with Estrin's scheme to
evaluate the numerator/denominator polynomials provides both a
sufficient numerical precision and a high degree of ILP, potentially
leading to a reduced run\-/time when executed on an appropriate CPU.
A corresponding approximant and a C implementation have been proposed
and compared to several existing implementations w.r.t.\ their
run\-/time.  The C implementation of the presented approximant can be
found in the appendix.  C++, Fortran, Julia and Rust implementations
can be found in \cite{polylogarithm,PolyLog.jl,polylog}, respectively.

>>>>

In the following an ILP-aware implementation of the real dilogarithm
with double precision is presented, which allows for the simultaneous
execution of multiple floating\-/point operations.  The real
dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\ln(1-t)}{t} \, \textnormal{d}t, &
  &x<1.
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
  \label{eq:series}
\end{align}
%
Further series representations exist, for example the accelerated
series
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\ln(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A series representation in
terms of Chebyshev polynomials of the first kind $T_n(x)$ is given in
\cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n(2x-1),
  \label{eq:cheby}
\end{align}
%
which is used for example in the ROOT program library \cite{root}.
The r.h.s.\ of Eqs.~\eqref{eq:series}--\eqref{eq:cheby} can be summed,
for example, using Horner's scheme or Clenshaw's algorithm
\cite{clenshaw}, respectively.  These summation techniques are,
however, purely sequential and thus do not make use of ILP.  In the
following an approximant of the real dilogarithm is presented, which
makes use of ILP, using a rational function approximation in
combination with Estrin's scheme, similar to the approach used in
Eq.~\eqref{eq:mixed}.

@@

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level (ILP) parallelism.  We found that a
rational minimax approximant in combination with Estrin's scheme to
evaluate the numerator/denominator polynomials provides both a
sufficient numerical precision and a high degree of ILP, potentially
leading to a reduced run\-/time when executed on a appropriate CPUs.
A corresponding approximant and a C implementation have been proposed
and compared to several existing implementations w.r.t.\ their
run\-/time.  The C implementation of the presented approximant can be
found in the appendix.  C++, Fortran, Julia and Rust implementations
can be found in \cite{polylogarithm,PolyLog.jl,polylog}, respectively.
